\cvsection{Experience}
\begin{cventries}
	
		\cventry
	{Chief Operating Officer, National Sensor Hub}
	{ANDHRA PRADESH MEDTECH ZONE LTD}
	{Visakhapatnam}
	{Mar. 2021 - Prsent}
	{
		\begin{cvitems}
			\item {Setting up of Centre to produce Medical grade sensors to be used in Medical Devices}
			\item { Helping startups to realise their products }
		\end{cvitems}
	}

	\cventry
	{Scientist-C}
	{AIC-AMTZ Medi Valley Incubation Council}
	{Visakhapatnam}
	{Mar. 2021 - Feb.2022}
	{
		\begin{cvitems}
			\item {To provide professional support to the startups in prototuping,sourcing etc..}
			\item { Establishing Medi Valley Laboratory in accordance with ISO 17025 for NABL Accreditation on Testing lab }
			\item {Supporting startups for compliance to ISO Standards (IEC 60601-1 , IEC 60601-1-2).}
			\item {Indigenization Medical Devices such as OT Lights,AED and Syring Pumps}
			\item {Program Manger for innovation calls.}
		\end{cvitems}
	}
	\cventry
	{Scientist-C}
	{Bio Valley Incubation Council}
	{Visakhapatnam}
	{Oct. 2020 - Mar. 2021}
	{
		\begin{cvitems}
			\item { Product development on Perfusion Device and Portable vaccine last mile devices}
			\item {Mentored starups on product development.}
			\item {Instrumental in validation,testing and Production of O2C for COVID 19 assentials.}
			\item {Setting up of Cryo Air Seperation Unit 100Cu Mtrs per Hour Plant in peak for COVID 19 assentials.}
		\end{cvitems}
	}

	\cventry
	{Scientist-C}
	{AIC-AMTZ Medi Valley Incubation Council}
	{Visakhapatnam}
	{May. 2020 - Oct. 2020}
	{
		\begin{cvitems}
			\item {To provide professional support to the startups in prototuping,sourcing etc..}			
			\item {Head for Pre Compliance Testing of Medical Devices and Calibration Labs at Medi Valley.}	
			\item {Instrumental in validation,testing and Production of Ventilators for COVID 19 assentials.}
			\item {Industry Relation Officer for CoE Medical Electonics and Bio Physics funded by meitY.}
		\end{cvitems}
	}


	\cventry
    {Research Fellow}
	{AIC-AMTZ Medi Valley Incubation Council}
	{Visakhapatnam}
	{Oct. 2019 - May 2020}
	{
		\begin{cvitems}
			\item {To provide professional support to the startups in prototuping,sourcing etc..}
			\item { Learned Pre Compliance Testing of Medical Devices.}
			\item { Learned Medical devices calibration in accordance ISO-IEC Standards.}
		\end{cvitems}
	}

 \cventry
    {Research Fellow}
    {KALAM INSTITUTE OF HEALTH TECHNOLOGY -KIHT}
    {Visakhapatnam}
    {May. 2019 - Oct. 2019}
    {
      \begin{cvitems}
        \item {To provide professional support to the startups in prototuping,sourcing etc..}
        \item {Product development mentoring.}
      \end{cvitems}
    }

  \cventry
    {Intern at Investments and Community Development}
    {INNOVATION VALLEY(AP INNOVATION SOCIETY)}
    {Visakhapatnam}
    {Jan. 2019 - May.2019}
    {
      \begin{cvitems}
        \item {To provide professional councling to ideation Startups and engaging the startup community with different activities.}
        \item {Conducting Startup onboarding Events and Webinars.}
        \item {Program Manger for the Wadhwani Venture FasTrack Acceleration Program.}
      \end{cvitems}
    }

  \cventry
    {Fablab Manager}
    {Makers Library}
    {Bhimavaram}
    {Aug. 2017 - Jul. 2018}
    {
      \begin{cvitems}
        \item {Paper work related to getting approval for Fablab and classification of Tools and Machinary for Purchase}
	\item{Idea behind Makers Library to setup APs First FABLAB to bring the Fab community into Rural area.}
        \item {supporting makers and innovators to bring their ideas to reality.}
      \end{cvitems}
    }

  \cventry
    {Research Assistant}
    {VSM Research and Consultancy Center}
    {Ramachandrapuram}
    {Jan. 2016 - Dec. 2016}
    {
      \begin{cvitems}
        \item {Provide professional consulting services to students and Faculty.}
	\item{Develop,maintain and teach courses ,support and supervise internships and research work.}
        \item {Management of Laboratory Equipment Asset Inventory.}
      \end{cvitems} 
    }
  \cventry
    {Live Ambassador}
    {Hackster.io USA}
    {Andhra Pradesh}
    {Jul. 2015 - Jun. 2017}
    {
      \begin{cvitems}
        \item {Hackster Ambassdors run live events that benefit local communities of Hardware and Software Developers.}
	\item{Conducted workshops on Amazon Alexa Skill Building,Microsoft Azure IoT Platfrom,NXP Freedom Boards.}
      \end{cvitems}
    }
  \cventry
    {Founder}
    {Makers Hive}
    {Ramachandrapuram}
    {Dec. 2013 - Feb. 2015}
    {
      \begin{cvitems}
        \item {I started a Small Makerspace at my home to build customized projects and Promoting DIY (Do it Yourself) projects among student Community. }
	\item{Trained students to build their projects and understand how to make an idea to reality.}
      \end{cvitems}
    }
\end{cventries}
