\cvsection{Extracurricular Activity}
\begin{cventries}
\cventry
    {Participating Member }
    { American Society for Testing and Materials (ASTM International)}
    {Membership No :2376533 }
    {March. 2022 - Present}
{
	 \begin{cvitems}
	\item {Electronics; Declarable Substances in Materials; 3D Imaging Systems; Additive Manufacturing Technologies}
	\item {Medical and Surgical Materials and Devices}
	\end{cvitems}
}
\cventry
    {Regular Fellow Member }
    { Optical Society of India (OSI)}
    {Membership No : 1760}
    {Nov. 2021 - Present}
{
 \begin{cvitems}
\end{cvitems}
}
\cventry
    {Early Career Professional Member}
    {Society of Photo-Optical Instrumentation Engineers (SPIE)}
    {Membership No : 4353307}
    {Oct. 2021 - Present}
{
 \begin{cvitems}
\item {Lithography ,Instruments and sensors   }
\item {Biomedical Optics  }
\item {Micro/Nanopatterning, Materials, and Metrology }
\end{cvitems}
}
\cventry
    {Early Career	 Member}
    {Optica – Earlier known as Optical Society of America (OSA)}
    {Membership No :1957146 }
    {Oct. 2021 - Present}
{
 \begin{cvitems}
\item {BB Optical Biosensors   }
\item {FL Lasers in Manufacturing }
\item {PO Optoelectronics }
\end{cvitems}
}
\cventry
    {Professional Member}
    {Association for Computing Machinery (ACM)}
    {Membership No :7633367 }
    {May. 2019 - Present}
{
 \begin{cvitems}
\end{cvitems}
}
  \cventry
    { Member-Vizag bay  Section}
    {Institute of Electrical and Electronics Engineers (IEEE)}
    {Membership No: 92553561}
    {Jan. 2015 - Present}
    {
      \begin{cvitems}
	\item {IEEE Electronics Packaging Society.}
	\item {IEEE Electron Devices Society (EDS).}
        \item {IEEE Computer Society Member.}
        \item {IEEE Education Society Member.}
        \item {IEEE Robotics and Automation Society Member.}
        \item {IEEE Technology and Engineering Management Society Member.}
        \item {Life Sciences Community, IEEE.}
        \item {Internet of Things Community, IEEE.}
      \end{cvitems}
    }
  
  \cventry
    {Early Profesional Member}
    {The American Society of Mechanical Engineers(ASME)}
    {Membership No:102240909}
    {Apr. 2018 - PRESENT}
{
}
  \cventry
    {Graduate Student Member}
    {Society of Automotive Engineers India (SAEI)}
    {Membership No : 7180429297}
    {Sep. 2017 - Mar. 2019}
{
 \begin{cvitems}
\end{cvitems}
}
\end{cventries}
