\cvsection{Education}
\begin{cventries}
  \cventry
    {Master of Technology in Advanced Manufacturing Systems}
    {VISHNU INSTITUTE OF TECHNOLOGY,BHIMAVARAM,A.P}
    {62.78\%}
    {Aug. 2017 - PRESENT}
    {
      \begin{cvitems}
        \item {Building a Cyber Physical Systems-Digital Twins (Project work in progress)}  
      \end{cvitems}
    }
  \cventry
    {Diploma in Principles and Applications of Digital Fabrication}
    {FABLAB KERALA,TRIVANDRUM,KERALA}
    {Graduated}
    {Jan. 2017 - Jul. 2017}
    {
      \begin{cvitems}
        \item {Developed a Fab Data Glass as part of the Program }
      \end{cvitems}
    }
  \cventry
    {Bachelor of Technology in Mechanical Engineering}
    {VSM COLLEGE ENGINEERING,RAMACHANDRAPURAM ,A.P}
    {64.91\%}
    {Aug. 2012 - Jul. 2017}
    {
      \begin{cvitems}
        \item {Designed and Developed a 3D Printer Prototype }
        \item {Implemented prototype was used in the Research and Consultancy Center.}
      \end{cvitems} 
    }
  \cventry
    {Specializing in Mathematics Physics and Chemistry}
    {G.R.C JUNIOR COLLEGE,RAMACHANDRAPURAM,A.P}
    {87.4\%}
    {Jul. 2010 - Jun. 2012}
    {
      \begin{cvitems}
	\item{Selected for DST-SEATS-INSPIRE PROGRAM INTERNSHIP SCIENCE CAMP}
        \item {Won Young Scientist Award,District Level 19th National Children's Science Congress.}
      \end{cvitems}
    }
  \cventry
    {Specializing in mathematics and science.}
    {SmtG.M.D MODERN HIGH SCHOOL,RAMACHANDRAPURAM,A.P}
    {86.16\%}
    {Jul. 2009 - Mar. 2010}
    {
      \begin{cvitems}
        \item {Won Jana vignana vedika(A.P) District Level Chekumuki Science Talent Test.}
      \end{cvitems}
}
\end{cventries}
