\cvsection{Experience}
\begin{cventries}
 \cventry
    {Scientist-C}
    {AIC-AMTZ Medi Valley Incubation Council}
    {Visakhapatnam}
    {May. 2019 - Present}
    {
      \begin{cvitems}
        \item {To provide professional support to the startups in prototuping,sourcing etc..}
        \item {Pre Compliance Testing of Medical Devices.}
        \item {Program Manger for the Wadhwani Venture FasTrack Acceleration Program.}
      \end{cvitems}
    }
  \cventry
    {Intern at Investments and Community Development}
    {INNOVATION VALLEY(AP INNOVATION SOCIETY)}
    {Visakhapatnam}
    {Jan. 2019 - May.2019}
    {
      \begin{cvitems}
        \item {To provide professional councling to ideation Startups and engaging the startup community with different activities.}
        \item {Conducting Startup onboarding Events and Webinars.}
        \item {Program Manger for the Wadhwani Venture FasTrack Acceleration Program.}
      \end{cvitems}
    }
  \cventry
    {Fablab Manager}
    {Makers Library}
    {Bhimavaram}
    {Aug. 2017 - Jul. 2018}
    {
      \begin{cvitems}
        \item {Paper work related to getting approval for Fablab and classification of Tools and Machinary for Purchase.}
	\item{Idea behind Makers Library to setup APs First FABLAB to bring the Fab community into Rural area.}
        \item {supporting makers and innovators to bring their ideas to reality.}
      \end{cvitems}
    }
  \cventry
    {Research Assistant}
    {VSM Research and Consultancy Center}
    {Ramachandrapuram}
    {Jan. 2016 - Dec. 2016}
    {
      \begin{cvitems}
        \item {Provide professional consulting services to students and Faculty.}
	\item{Develop,maintain and teach courses ,support and supervise internships and research work.}
        \item {Management of Laboratory Equipment Asset Inventory.}
      \end{cvitems} 
    }
  \cventry
    {Live Ambassador}
    {Hackster.io USA}
    {Andhra Pradesh}
    {Jul. 2015 - Jun. 2017}
    {
      \begin{cvitems}
        \item {Hackster Ambassdors run live events that benefit local communities of Hardware and Software Developers.}
	\item{Conducted workshops on Amazon Alexa Skill Building,Microsoft Azure IoT Platfrom,NXP Freedom Boards.}
      \end{cvitems}
    }
  \cventry
    {Founder}
    {Makers Hive}
    {Ramachandrapuram}
    {Dec. 2013 - Feb. 2015}
    {
      \begin{cvitems}
        \item {I started a Small Makerspace at my home to build customized projects and Promoting DIY (Do it Yourself) projects among student Community. }
	\item{Trained students to build their projects and understand how to make an idea to reality.}
      \end{cvitems}
    }
\end{cventries}
