\cvsection{Extracurricular Activity}
\begin{cventries}
  \cventry
    {Graduate Student Member-Vizag Bay Subsection}
    {IEEE}
    {Member number: 92553561}
    {Jan. 2015 - Present}
    {
      \begin{cvitems}
        \item {IEEE Computer Society Member.}
        \item {IEEE Education Society Member.}
        \item {IEEE Robotics and Automation Society Member.}
        \item {IEEE Technology and Engineering Management Society Member.}
        \item {Life Sciences Community, IEEE.}
        \item {Internet of Things Community, IEEE.}
      \end{cvitems}
    }
  \cventry
    {Member}
    {PLUS (Laboratory for UNIX Security in POSTECH)}
    {Pohang, S.Korea}
    {Sep. 2010 - Oct. 2011}
    {
      \begin{cvitems}
        \item {Gained expertise in hacking \& security areas, especially about internal of operating system based on UNIX and several exploit techniques.}
        \item {Participated on several hacking competition and won a good award.}
        \item {Conducted periodic security checks on overall IT system as a member of POSTECH CERT.}
        \item {Conducted penetration testing commissioned by national agency and corporation.}
      \end{cvitems}
    }
  \cventry
    {Member}
    {MSSA (Management Strategy Club of POSTECH)}
    {Pohang, S.Korea}
    {Sep. 2013 - PRESENT}
    {
      \begin{cvitems}
        \item {Gained knowledge about several business field like Management, Strategy, Financial and marketing from group study.}
        \item {Gained expertise in business strategy areas and inisght for various industry from weekly industry analysis session.}
      \end{cvitems}
    }
\end{cventries}
