\cvsection{Projects}
\begin{cventries}
  \cventry
    {Maker}
    {FAB DATA GLASS}
    {FAB ACADEMY}
    {Jun. 2017}
    {
      \begin{cvitems}
        \item {A Low Cost Augmented display,to know the current temprature and Humidity ,Pressure and Altitude and Light Intensity data with out looking into the mobile while working.which uses the DHT11,BMP180 ,LDR Reading for Lux values.which was built using five process 3D Printing,CNC PCB Milling,Vinyl Cutter,LASER Cutting and LASER Engraving  as per the requirement of the Fab academy. }
      \end{cvitems}
    }
   \cventry
    {Team Member}
    {SMILE - Sustainable modular intelligent lighting everywhere}
    {STEAM SCHOOL}
    {Dec. 2016}
    {
      \begin{cvitems}
        \item {The solution that our team came up with at the end of S.T.E.A.M school is a smart lighting pole. From the design aspect, the pole is modular especially the seating and can be deployed to the present solutions like using the solar panel, condenser, IoT solution separately. Second comes the sustainability factor where the whole structure is made of recycled aluminium, lastly from the intelligent aspect, it has a SOS buttom which sends a tweet with location, time stamp, date stamp and predefined hash tags and twitter handles in case of emergency, it also has a ambient light sensor that switches on the light using a relay only when it is needed, thus saving a lot of energy. All the module under the solar panel is designed in such a way that it collects moisture fromthe air and through capillary action the dew drops are used to wipe dust on the solar module effectively, thus increase in total efficiency.}
      \end{cvitems}
    }
  \cventry
    {Team Leader}
    {Advanced Rapid Prototying Device 3D Printer}
    {Under Graduation Project}
    {Apr. 2016}
    {
      \begin{cvitems}
        \item {we have implimented the Advanced rapid prototyping device '3D Printer ' as part of the final year project ,we have used the fastbot3d BBBP 1S board to get high and accurate results for the 3D printing and also we have achived the remotely controlling the 3D printer.}
      \end{cvitems}
    }
  \cventry
    {Team Member}
    {LOW COST BRAILLE PRINTER}
    {LVPEI-MIT REDX }
    {Jun. 2014}
    {
      \begin{cvitems}
        \item { Low Cost Braille Printer at ReDx workshop under the guidance of Dr. Elliott Rouse, Post-Doctoral Fellow at MIT Media Lab (Massachusetts Institute of Technology).This project is undertaken to develop a low cost portable braille printer because the present printer which is in market is so expensive.}
      \end{cvitems}
    }
\end{cventries}